Centers and centralizers of higher enveloping algebras of Lie algebras

### 2020-09-08 draft.tex
fixes with owen

@@

When $k$ is $\RR$ or $\CC$, 
the enveloping $E_n$ algebra $\UU_n \fg$ of a dg Lie algebra $\fg$ is modeled by the locally constant factorization algebra $\bU_n \fg$ that assigns
\[
\bU_n \fg(V) = \cliels(\Omega^*_c(V) \otimes \fg)
\]
to each open set $V \subset \RR^n$.
\end{thm}

@@

\begin{dfn}\label{dfn:pair}
A {\em factorization pair} on a manifold $M$ is a pair $(\bB, \bM)$ where
\begin{itemize}
\item $\bB$ is an $\EE_1$-algebra in locally constant factorization algebras;
\item $\bM$ is a locally constant factorization algebra together with map of $\EE_1$ factorization algebras $\bB \to \bZ_n(\bM)$.
\end{itemize}
\end{dfn}

@@

\owen{Somewhere please mention that the slogan ``quantization commutes with pushforward'' holds for this class of theories.}

@@

\begin{prp} \label{prp:swiss1}
Let $\fg$ be a Lie algebra. 
The pair $(\fZ_n(\fg) , \UU_n(\fg))$ is a filtered object in the $\infty$-category of algebras over the $(n+1)$-dimensional Swiss cheese operad. 
The resulting associated graded pair $({\rm Gr} \; \fZ_n(\fg) , {\rm Gr} \; \UU_n(\fg))$ is a commutative algebra object.
\end{prp}

The key insight is that there exists a filtration on our model for the $\EE_n$-center $\bZ_n(\fg)$ and the $\EE_n$-enveloping algebra $\bU_n (\fg)$ whose associated graded factorization algebras ${\rm Gr} \; \bZ_n(\fg)$ and ${\rm Gr} \; \bU_n(\fg)$ are commutative factorization algebras.

Given a filtered associative algebra whose associated graded is commutative, there exists a Poisson bracket on the associated graded algebra. 
If the associated graded of a filtered $\EE_n$-algebra is commutative, then it carries the structure of a $\PP_n$-algebra, which is similar to a Poisson algebra except the bracket is of cohomological degree $1-n$. 
There is a similar description of the ``classical limit"  of algebras over the $(n+1)$-dimensional Swiss cheese operad in terms of algebras over a certain two-colored operad $\PP_{[n+1,n]}$, see \cite{Pavel1, Pavel2}. 
We recall the definition of this operad below.

@@

\begin{rmk}
By a similar proof as in the main part of the paper, we expect that one can see that the factorization algebra
\[
\clie \bigg(\Omega^\bu \otimes \fg \; ; \; {\rm Sym} \left(\Omega^\bu_c \otimes \fg [1] \right) \bigg)
\]
is a model for the {\em $\PP_n$-center} of the $\PP_n$-enveloping algebra $\UU_{\PP_n} (\fg)$. 
\end{rmk}

@@

Any constructible factorization algebra $\bA$ on $M \times \RR_{\geq 0}$ determines a factorization pair $(\pi_* \overset{\circ}{\bA} , \bA_{\partial})$ in the sense of Definition \ref{dfn:pair}.
We recall this construction in Section \ref{sec:bulk}. 
In particular, on the upper half space $\HH^n$, a constructible factorization algebra determines an algebra over the $(n+1)$-dimensional Swiss cheese operad.

@@

\begin{prp}\label{prp:pair}
Let $M$ be a smooth $n$-dimensional manifold and $\fg$ a Lie algebra. 
There is a constructible commutative factorization algebra ${\bf C}_n (\fg)$
%\begin{equation}\label{eqn:graded}
%\left({\bf Bulk}_n (\fg) \; , \; {\rm Gr} \; \bU_n(\fg) \right)
%\end{equation}
on $M \times \RR_{\geq 0}$ such that the pair 
\[
(\pi_* \overset{\circ}{\bf C}_n (\fg), {\bf C}_n (\fg)_\partial)
\]
is equivalent to the pair $({\rm Gr} \; \bZ_n(\fg), {\rm Gr} \; \bU_n(\fg))$ as commutative factorization algebras \brian{adjectives}
\end{prp}

@@

Following the proof of this proposition, our main thrust is to interpret this result by exhibiting a topological field theory on the $(n+1)$-dimensional manifold with boundary $M \times \RR_{\geq 0}$ whose factorization algebra of classical observables is precisely the constructible factorization algebra in (\ref{eqn:graded}).

The Batalin--Vilkovisky (BV) formalism for studying quantum field theory \brian{finish}

\brian{as a corollary butson-yoo}

@@

For any dg Lie (in fact, $L_\infty$) algebra, the Chevalley--Eilenberg cochain complex computing Lie algebra homology admits a natural filtration whose associated graded has the structure of a commutative dg algebra.
If $\fh$ is a dg Lie algebra, let $\clieu_{\leq k} (\fh)$ be the subcomplex of Chevalley--Eilenberg chains which is $\Sym^{\leq k} (\fh[1])$ as an underlying graded vector space. 
The associated graded cochain complex is the free symmetric algebra on $\fh[1]$ thought of as simply a cochain complex:
\[
{\rm Gr} \; \clieu (\fh) = {\rm Sym} (\fh [1])  .
\]
Here, the differential on the right-hand side is simply the underlying linear differential of $\fh$ (in terms of $L_\infty$ algebras, this is the $1$-ary operation $\ell_1$).

@@

There is a similar filtration on our model for the $\EE_n$-center $\bZ_n(\fg)$ defined by
\[
F^k \bZ_n(\fg) = \clie \bigg(\fg \otimes \Omega \; , \; \clieu_{\leq k} (\fg \otimes \Omega_c) \bigg) .
\]

@@

@@

\begin{dfn}
For an open set $U \subset M \times \RR_{>0}$ let $\overset{\circ}{\bC}_n(\fg) (U)$ be the cochain complex 
\[
\overset{\circ}{\bC}_n (\fg) (U) = \clie \bigg(\fg \otimes \Omega (U) \; , \; \Sym \left(\fg \otimes \Omega_c(U) [2] \right) \bigg) .
\]
\end{dfn}

The assignment $U \mapsto \overset{\circ}{\bC}_n(\fg)(U)$ defines a locally constant factorization algebra on $M \times \RR_{>0}$. 
In fact, it extends to a constructible factorization algebra on $M \times \RR_{\geq 0}$ in the following way.

To state the definition, we will make use of the following map of cochain complexes.

\begin{dfn}\label{dfn:constructible1}
Let $\bC_n(\fg)$ be the following constructible $\PP_0$-factorization algebra on $M \times \RR_{\geq 0}$:
\begin{itemize}
\item to an open set $U \subset M \times \RR_{> 0}$, we assign the cochain complex $\overset{\circ}{\bC}_n (\fg)(U)$.
\item to an open set $V \times [0,\epsilon)$ we assign the cochain complex ${\rm Gr} \;\bU_n(\fg)(V)$. 
\end{itemize}
The structure map associated to the embedding 
\[
U \sqcup V \times [0, \epsilon) \hookrightarrow V' \times [0,\epsilon')
\]
is
\[
\clie \bigg(\fg \otimes \Omega^\bu (U) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \bigg) \; \otimes \;  {\rm Sym} \left(\fg \otimes \Omega^\bu_c (V) [1] \right) 
\]
\end{dfn}

@@

\begin{lmm}
$\bC_n(\fg)$ has the structure of a constructible $\PP_0$-factorization algebra on $M \times \RR_{\geq 0}$. 
\end{lmm}
\begin{proof}
Note that as an underlying graded vector space $\Tilde{\bZ}_n(\fg) (U)$ is of the form
\[
{\rm Sym} \left(\fg^* \otimes \Bar{\Omega}_c (U) [n-1] \right) \; \Hat{\otimes} \; {\rm Sym}  \left(\fg \otimes \Omega_c(U) [2] \right)  .
\]
Let $x^* \otimes \alpha$ denote an element of $\fg \otimes \Bar{\Omega}_c (U)$ and $y \otimes \beta$ denote an element of $\fg \otimes \Omega_c(U) [2]$. 
Then, the bracket involving the linear elements $(x^* \otimes \alpha) \otimes 1$ and $1 \otimes (y \otimes \beta)$ is defined by
\begin{align*}
\{(x^* \otimes \alpha) \otimes 1 , 1 \otimes (y \otimes \beta)\} & = \<x^*, y\>_\fg \int_U \alpha \beta \\
\{(x^* \otimes \alpha) \otimes 1 , (x'^* \otimes \alpha') \otimes 1\} & = 0 \\
\{1 \otimes (y \otimes \beta) , 1 \otimes (y' \otimes \beta')\} & = 0 . 
\end{align*}
Here, $\<x^*, y\>_\fg$ denotes the linear pairing between $\fg$ and $\fg^*$ and $\int_U\alpha \beta$ denotes the linear pairing between compactly supported distributional differential forms and differential forms. 
The bracket is extended to the entire symmetric algebra by using the graded Leibniz rule.
\end{proof}

Suppose $\bA$ is any constructible factorization algebra on a manifold with boundary $M \times \RR_{\geq 0}$. 
Then, restricting to the boundary $M$, we obtain a locally constant factorization algebra that we will denote by $\bA_{\partial}$. 
Likewise, we can restrict to the bulk $M \times \RR_{> 0}$ and pushforward along $\pi : M \times \RR_{> 0} \to M$ to obtain another locally constant factorization algebra on $M$ that we will denote by $\pi_* \overset{\circ}{\bA}$. 
It is immediate to check that $(\pi_* \overset{\circ}{\bA} , \bA_{\partial})$ form a factorization pair in the sense of Definition \ref{dfn:pair}.

 \begin{lmm}
Let $M$ be an $n$-dimensional manifold.
There is a quasi-isomorphism of  $\PP_0$-factorization algebras on $M$:
\[
\pi_* \overset{\circ}{\bf Z}_n(\fg) \; \xto{\simeq} \; {\rm Gr} \; \bZ_n(\fg) .
\]
where $\pi : M \times \RR_{>0} \to M$ is the projection. 
\end{lmm}

@@

@@

@@

For any Lie algebra $\fg$, there is a topological field theory defined in any dimension known as ``topological BF theory". 
Suppose $N$ is an $(n+1)$-dimensional manifold, which for now we assume has no boundary $\partial N = \emptyset$. 
In the BV formalism, the perturbative space of fields of BF theory on $N$ consists of
\[
(A, B) \in \Omega^{\bu} (N) \otimes \fg [1] \oplus \Omega^{\bu} (N) \otimes \fg^* [n-1] .
\]
When $N$ is compact, the classical moduli space underlying this field theory has an elegant description in terms of the AKSZ formalism. 
It can be interpreted as the following mapping stack 
\begin{equation} \label{stack1}
{\rm Map}(N_{\rm dR} ,  {\rm T}^*[n] {\rm B} G)
\end{equation}
where $N_{\rm dR}$ denotes the de Rham stack of $N$ and where $G$ is a Lie group whose Lie algebra is $\fg$. 
Perturbative BF theory is obtained by taking the tangent space of the above mapping stack near at the trivial $G$-bundle.
Concretely, the classical moduli space consists of pairs $(A, B)$ where $A \in \Omega^1 (N) \otimes \fg$ and $B \in \Omega^{n-1} (N) \otimes \fg^*$ satisfying the equations
\begin{align*}
\d A + \frac12 [A,A] & = 0 \\
\d B + [A,B] & = 0 .
\end{align*}

Now, suppose $N$ has a boundary $\partial N \ne 0$.
Then, (\ref{stack1}) no longer admits a $(-1)$-shifted symplectic structure. 
However, the AKSZ construction equips 
\[
{\rm Map}(\partial N , {\rm T}^* [n] {\rm B} G)
\]
with a $0$-shifted symplectic structure. 
Perturbatively, this mapping stack represents the restriction of the fields to the boundary.

@@

\begin{dfn}
Let $M$ be an $n$-dimensional manifold.
{\em Topological BF theory with its universal Neumann boundary condition} is the classical bulk-boundary theory on $M \times \RR_{\geq 0}$ described as follows:
\begin{itemize}
\item[(1)] 
The bulk theory is that of topological BF theory on $M \times \RR_{>0}$, where the space of fields is 
\[
\cE|_{M \times \RR_{>0}} = \Omega^{\bu} (M \times \RR_{>0}) \otimes \fg [1] \oplus \Omega^{\bu} (M \times \RR_{>0}) \otimes \fg^* [n-2] .
\]
\item[(2)] 
The boundary condition is determined by the subspace of the fields on the boundary
\[
\Omega^{\bu} (M) \otimes \fg^* [n-2] \subset \cE|_{M \times \{0\}} .
\]
\end{itemize}
\end{dfn}

@@

\begin{prp}
The constructible $\PP_0$-factorization algebra of topological BF theory with its universal Neumann boundary condition is equivalent to the constructible factorization algebra $(\Tilde{\bZ}_n (\fg), {\rm Gr} \bU_n (\fg))$ of Definition \ref{dfn:constructible1}. 
\end{prp}

>>>>

\brian{notation $\EE$ and $\bE$}

@@

When $k$ is $\RR$ or $\CC$, 
the enveloping $E_n$ algebra $\UU_n \fg$ of a dg Lie algebra $\fg$ is modeled by the locally constant factorization algebra $\bU_n \fg$ that assigns
\[
\bU_n \fg(V) = \cliels(\Omega^\bu_c(V) \otimes \fg)
\]
to each open set $V \subset \RR^n$.
\end{thm}

@@

\begin{dfn}\label{dfn:pair}
A {\em factorization pair} on a manifold $M$ is a pair $(\bB, \bM)$ where
\begin{itemize}
\item $\bB$ is an associative algebra in locally constant factorization algebras;
\item $\bM$ is a locally constant factorization algebra together with map $\bB \to \bZ_n(\bM)$ of associative algebras in factorization algebras.
\end{itemize}
\brian{add remark about 1 categorical notion}
\end{dfn}

@@

@@

\begin{prp} \label{prp:swiss1}
Let $\fg$ be an $L_\infty$ algebra. 
The pair $(\fZ_n(\fg) , \UU_n(\fg))$ is a filtered object in the $\infty$-category of algebras over the $(n+1)$-dimensional Swiss cheese operad. 
The resulting associated graded pair $({\rm Gr} \; \fZ_n(\fg) , {\rm Gr} \; \UU_n(\fg))$ is a commutative algebra object.
\end{prp}

The key insight is that there exists a filtration on our model $\bZ_n(\fg)$ for the $\EE_n$-center and our model $\bU_n (\fg)$ for the $\EE_n$-enveloping algebra  whose associated graded factorization algebras ${\rm Gr} \; \bZ_n(\fg)$ and ${\rm Gr} \; \bU_n(\fg)$ are commutative factorization algebras.

Given a filtered associative algebra whose associated graded is commutative, there exists a Poisson bracket on the associated graded algebra. 
If the associated graded of a filtered $\EE_n$-algebra is commutative, then it carries the structure of a $\PP_n$-algebra, which is similar to a Poisson algebra except the bracket is of cohomological degree $1-n$. 
There is a similar description of the ``classical limit"  of algebras over the $(n+1)$-dimensional Swiss cheese operad in terms of algebras over a certain two-colored operad $\PP_{[n+1,n]}$, introduced by Safronov \cite{Pavel1, Pavel2}, whose definition we recall below.

@@

\begin{rmk}
By a similar proof as in the main part of the paper, we expect that one can see that the factorization algebra
\[
\clies \bigg(\Omega^\bu \otimes \fg \; ; \; {\rm Sym} \left(\Omega^\bu_c \otimes \fg [1] \right) \bigg)
\]
is a model for the {\em $\PP_n$-center} of the $\PP_n$-enveloping algebra $\UU_{\PP_n} (\fg)$. 
\end{rmk}

@@

Any constructible factorization algebra $\bA$ on $M \times \RR_{\geq 0}$ determines a factorization pair $(\bA^\circ , \bA^{\partial})$ in the sense of Definition \ref{dfn:pair}.
We recall this construction in Section \ref{sec:bulk}. 
In particular, on the upper half space $\HH^n$, a constructible factorization algebra determines an algebra over the $(n+1)$-dimensional Swiss cheese operad.

@@

\begin{prp}\label{prp:pair}
Let $M$ be a smooth $n$-dimensional manifold and $\fg$ a Lie algebra. 
There is a constructible commutative factorization algebra ${\bf C}_n (\fg)$
%\begin{equation}\label{eqn:graded}
%\left({\bf Bulk}_n (\fg) \; , \; {\rm Gr} \; \bU_n(\fg) \right)
%\end{equation}
on $M \times \RR_{\geq 0}$ such that the pair 
\[
\left( {\bf C}_n (\fg)^\circ \; , \; {\bf C}_n (\fg)^\partial \right)
\]
is equivalent to the pair $({\rm Gr} \; \bZ_n(\fg), {\rm Gr} \; \bU_n(\fg))$ as a commutative factorization pair.
\end{prp}

@@

Following the proof of this proposition, our main thrust is to interpret this result by exhibiting a topological field theory on the $(n+1)$-dimensional manifold with boundary $M \times \RR_{\geq 0}$ whose factorization algebra of classical observables is equivalent to the constructible factorization algebra $\bC_n(\fg)$. 
\brian{improve this pointer}
\owen{Somewhere please mention that the slogan ``quantization commutes with pushforward'' holds for this class of theories.}

%The Batalin--Vilkovisky (BV) formalism for studying quantum field theory \brian{finish}
%
%\brian{as a corollary butson-yoo}

@@

For any $L_\infty$ algebra, the Chevalley--Eilenberg cochain complex computing Lie algebra homology admits a natural filtration whose associated graded has the structure of a commutative dg algebra.
If $\fh$ is an $L_\infty$ algebra, let $\clieu_{\leq k} (\fh)$ be the subcomplex of Chevalley--Eilenberg chains which is $\Sym^{\leq k} (\fh[1])$ as an underlying graded vector space. 
The associated graded cochain complex is the free symmetric algebra on $\fh[1]$ thought of as simply a cochain complex:
\[
{\rm Gr} \; \cliels (\fh) = {\rm Sym} (\fh [1])  .
\]
Here, the differential on the right-hand side is simply the underlying linear differential of $\fh$ (in terms of $L_\infty$ algebras, this is the $1$-ary operation $\ell_1$).

@@

There is a similar filtration on our model for the $\EE_n$-center $\bZ_n(\fg)$ defined by
\[
F^k \bZ_n(\fg) = \clies \bigg(\fg \otimes \Omega \; , \; \clieu_{\leq k} (\fg \otimes \Omega_c) \bigg) .
\]

@@

\brian{define $\PP_0$ factorization algebra}

@@

\begin{dfn}
\label{dfn:constructible1}
Let $\bC_n(\fg)$ be the following constructible factorization algebra on $M \times \RR_{\geq 0}$:
\begin{itemize}
\item to an open set $U \subset M \times \RR_{> 0}$, we assign the cochain complex 
\[
\bC_n (\fg) (U) = \clies \bigg(\fg \otimes \Omega (U) \; , \; \Sym \left(\fg \otimes \Omega_c(U) [2] \right) \bigg) .
\]
\item to an open set $V \times [0,\epsilon)$ we assign the cochain complex 
\[
\bC_n (\fg) (V \times [0,\epsilon)) = {\rm Sym} \left(\fg \otimes \Omega^\bu_c (V \times [0,\epsilon) [2] \right).
\]
\end{itemize}
The structure map associated to the embedding 
\[
U \sqcup V \times [0, \epsilon) \hookrightarrow V' \times [0,\epsilon')
\]
is
\[
\clies \bigg(\fg \otimes \Omega^\bu (U) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \bigg) \; \otimes \;  {\rm Sym} \left(\fg \otimes \Omega^\bu_c (V\times [0,\epsilon)) [2] \right) 
\]
\brian{finish}
\end{dfn}

@@

\begin{lmm}
$\bC_n(\fg)$ has the structure of a constructible $\PP_0$-factorization algebra on $M \times \RR_{\geq 0}$. 
\end{lmm}

\begin{proof}
Note that as an underlying graded vector space $\Tilde{\bZ}_n(\fg) (U)$ is of the form
\[
{\rm Hom}^\bu\left(\Sym(\fg \otimes \Omega^\bu (U)[1]) \; , \; {\rm Sym}  \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \right)  .
\]
\brian{explain notation with homs} 
Let $x^* \otimes \alpha$ denote an element of $\fg \otimes \Bar{\Omega}_c (U)$ and $y \otimes \beta$ denote an element of $\fg \otimes \Omega_c(U) [2]$. 
Then, the bracket involving the linear elements $(x^* \otimes \alpha) \otimes 1$ 
and $1 \otimes (y \otimes \beta)$ is defined by
\begin{align*}
\{(x^* \otimes \alpha) \otimes 1 , 1 \otimes (y \otimes \beta)\} & = \<x^*, y\>_\fg \int_U \alpha \beta \\
\{(x^* \otimes \alpha) \otimes 1 , (x'^* \otimes \alpha') \otimes 1\} & = 0 \\
\{1 \otimes (y \otimes \beta) , 1 \otimes (y' \otimes \beta')\} & = 0 . 
\end{align*}
Here, $\<x^*, y\>_\fg$ denotes the linear pairing between $\fg$ and $\fg^*$ and $\int_U\alpha \beta$ denotes the linear pairing between compactly supported distributional differential forms and differential forms. 
The bracket is extended to the entire symmetric algebra by using the graded Leibniz rule.
\end{proof}

Next, we provide a construction of a factorization pair on the manifold $M$ from that data of a constructible factorization algebra on $M \times \RR_{\geq 0}$. 
Suppose $\bA$ is any constructible factorization algebra on a manifold with boundary $M \times \RR_{\geq 0}$. 
Let $\pi : M \times \RR_{\geq 0} \to M$ be the projection and denote by $\pi|_{M \times \RR_{>0}}$ its restriction to the interior. 
Define the following two factorization algebras on $M$:
\begin{align*}
\bA^\circ & = \left(\left.\pi\right|_{M \times \RR_{>0}} \right)_* \bA \\
\bA^\partial & = \pi_* \bA
\end{align*}
It is immediate to check that $(\bA^\circ, \bA^\partial)$ form a factorization pair in the sense of Definition \ref{dfn:pair}. 
In fact, this construction determines a functor from the category of constructible factorization algebras on $M \times \RR_{\geq 0}$ to factorization pairs on $M$.

 \begin{lmm}
 \brian{fix notation}
Let $M$ be an $n$-dimensional manifold.
There is a quasi-isomorphism of  $\PP_0$-factorization algebras on $M$:
\[
\pi_* \overset{\circ}{\bf Z}_n(\fg) \; \xto{\simeq} \; {\rm Gr} \; \bZ_n(\fg) .
\]
where $\pi : M \times \RR_{>0} \to M$ is the projection. 
\end{lmm}

@@

\brian{intro paragraph}

@@

\brian{maybe say AKSZ here}

@@

For any Lie algebra $\fg$, there is a topological field theory defined in any dimension known as {\em topological BF theory}.
Suppose $N$ is an $(n+1)$-dimensional manifold, which for now we assume has no boundary $\partial N = \emptyset$. 
In the BV formalism, the perturbative space of fields of topological $BF$ theory on $N$ consists of
\[
(A, B) \in \Omega^{\bu} (N) \otimes \fg [1] \oplus \Omega^{\bu} (N) \otimes \fg^* [n-1] .
\]
Concretely, the classical moduli space consists of pairs $(A, B)$ where $A \in \Omega^1 (N) \otimes \fg$ and $B \in \Omega^{n-1} (N) \otimes \fg^*$ satisfying the equations
\begin{align*}
\d A + \frac12 [A,A] & = 0 \\
\d B + [A,B] & = 0 .
\end{align*}
When $N$ is compact, the classical moduli space underlying this field theory has an elegant description in terms of the AKSZ formalism. 
It can be interpreted as the following mapping stack 
\begin{equation} \label{stack1}
{\rm Map}(N_{\rm dR} ,  {\rm T}^*[n] {\rm B} G)
\end{equation}
where $N_{\rm dR}$ denotes the de Rham stack of $N$ and where $G$ is a Lie group whose Lie algebra is $\fg$. 
Perturbative BF theory is obtained by taking the tangent space of the above mapping stack near at the trivial $G$-bundle.

Now, suppose $N$ has a boundary $\partial N \ne 0$.
Then, (\ref{stack1}) no longer admits a $(-1)$-shifted symplectic structure. 
However, the AKSZ construction equips 
\[
{\rm Map}(\partial N_{\rm dR} , {\rm T}^* [n] {\rm B} G)
\]
with a $0$-shifted symplectic structure. 
Perturbatively, this mapping stack represents the restriction of the fields to the boundary.

@@

\begin{dfn}
Let $M$ be an $n$-dimensional manifold.
{\em Topological BF theory with its universal Neumann boundary condition} is the classical bulk-boundary theory on $M \times \RR_{\geq 0}$ described as follows:
\begin{itemize}
\item[(1)] 
The bulk theory is topological BF theory on $M \times \RR_{>0}$, where the space of fields is 
\[
\cE|_{M \times \RR_{>0}} = \Omega^{\bu} (M \times \RR_{>0}) \otimes \fg [1] \oplus \Omega^{\bu} (M \times \RR_{>0}) \otimes \fg^* [n-2] .
\]
\item[(2)] 
The boundary condition is the Lagrangian subspace
\[
\Omega^{\bu} (M) \otimes \fg^* [n-2] \subset \cE|_{M \times \{0\}} .
\]
\end{itemize}
\end{dfn}

@@

\begin{prp}
The constructible $\PP_0$-factorization algebra of topological BF theory with its universal Neumann boundary condition is equivalent to the constructible factorization algebra $\bC_n(\fg)$. 
\end{prp}

\begin{rmk} Examples

Poisson $\sigma$-model. 
$B$-model. 
cite paper with Eugene.
Kapustin-Witten. 
\end{rmk}

\subsection{Factorization homology on manifolds with boundary}
